Privacy-Respecting Type Error Telemetry at Scale

### 2024-01-31 programming23/paper.tex
update clsfile, cite artifact

% TODO BEFORE FINAL
% - update all refs to artifacts to no longer be in future tense

@@

\documentclass[english,cleveref]{programming}
%% use 'submission' for initial submission, remove it for camera-ready (see 5.1)

@@

%%%%%%%%%%%%%%%%%%
\paperdetails{
  %% perspective options are: art, sciencetheoretical, scienceempirical, engineering.
  %% Choose exactly the one that best describes this work. (see 2.1)
  perspective=scienceempirical,
  %% State one or more areas, separated by a comma. (see 2.2)
  %% Please see list of areas in http://programming-journal.org/cfp/
  %% The list is open-ended, so use other areas if yours is/are not listed.
  area={Data mining for programming, Telemetry},
  %% You may choose the license for your paper (see 3.)
  %% License options include: cc-by (default), cc-by-nc
  % license=cc-by,
}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
%% These data are provided by the editors. May be left out on submission.
%\paperdetails{
%  submitted=2023-1-31,
%  published=2016-10-11,
%  year=2016,
%  volume=1,
%  issue=1,
%  articlenumber=1,
%}
%%%%%%%%%%%%%%%%%%

@@

\author[a,b]{Ben Greenman}
\authorinfo{(\email{benjamin.l.greenman@gmail.com}) was a CIFellows 2020
postdoc at Brown University and is now an assistant professor in the
Kahlert School of Computing at the University of Utah.}
\affiliation[a]{Brown University, Providence, RI, USA}
\affiliation[b]{University of Utah, Salt Lake City, UT, USA}
% \orcid{0000-0001-7078-9287}

@@

\author[c]{Mitesh Shah}
\authorinfo{(\email{mshah@roblox.com}) is Senior Engineering Director, Programmability, at Roblox.}

@@

  \paragraph{Grounding}
  %% What argument, feasibility proof, artifacts,
  %% or results and evaluation support this work?
  Our findings are supported by a dataset
  of over 1.5 million telemetry records.
  The data and scripts for analyzing it will be available in an artifact.

@@

\begin{figure}[t]\centering
  %% TODO weird artifact (|) in x-min label
  %% code/row-distribution.rkt
  \includegraphics[width=\columnwidth]{img/row-distribution.pdf}
  \begin{tabular}{ll}
    Reason for sending:
    &
    \begin{tabular}[t]{r@{~~}l@{~~}r}
      996,164 & due to keystrokes  & [\pct{66.20}] \\
      508,572 & due to module switch & [\pct{33.80}]
    \end{tabular}
  \end{tabular}
  \caption{Telemetry records per hour. Each tick on the $x$-axis marks the start of a new day in California. Shaded ranges correspond to weekends.}
  \label{f:records-per-hour}
\end{figure}

@@

>>>>

@@

\documentclass[crc,english,cleveref]{programming}

@@

%%% The following is specific to Programming Journal, Volume 8, Issue 3 and the paper
%%% 'Privacy-Respecting Type Error Telemetry at Scale'
%%% by Ben Greenman, Alan Jeffrey, Shriram Krishnamurthi, and Mitesh Shah.
%%%
\paperdetails{
  submitted=2023-10-01,
  published=2024-02-15,
  year=2024,
  volume=8,
  issue=3,
  articlenumber=12,
}

@@

\author[a,b]{Ben Greenman}
\authorinfo{(\email{benjamin.l.greenman@gmail.com}) was a CIFellows 2020
postdoc at Brown University and is now an assistant professor in the
Kahlert School of Computing at the University of Utah.}
% \orcid{0000-0001-7078-9287}
\affiliation[a]{Brown University, Providence, RI, USA}
\affiliation[b]{University of Utah, Salt Lake City, UT, USA}

@@

\author[c]{Mitesh Shah}
% \orcid{0009-0000-6084-123X}
\authorinfo{(\email{mshah@roblox.com}) is Senior Engineering Director, Programmability, at Roblox.}

@@

  \paragraph{Grounding}
  %% What argument, feasibility proof, artifacts,
  %% or results and evaluation support this work?
  Our findings are supported by a dataset
  of over 1.5 million telemetry records.
  The data and scripts for analyzing it are available in an artifact.

@@

\begin{figure}[t]\centering
  %% TODO weird artefact (|) in x-min label
  %% code/row-distribution.rkt
  \includegraphics[width=\columnwidth]{img/row-distribution.pdf}
  \begin{tabular}{ll}
    Reason for sending:
    &
    \begin{tabular}[t]{r@{~~}l@{~~}r}
      996,164 & due to keystrokes  & [\pct{66.20}] \\
      508,572 & due to module switch & [\pct{33.80}]
    \end{tabular}
  \end{tabular}
  \caption{Telemetry records per hour. Each tick on the $x$-axis marks the start of a new day in California. Shaded ranges correspond to weekends.}
  \label{f:records-per-hour}
\end{figure}

@@

\paragraph{Data Availability Statement}

The artifact for this paper contains the full telemetry dataset
and scripts for reproducing the analysis in~\cref{s:data}.
The source code for the paper itself is available through Software
Heritage~\cite{luau-swhid}.
